Case Study (McKenna)

### 2020-04-09 Code/mrp/Case Study (McKenna) .Rmd
Working on simple logit model

```
```{r}
fit %>%
  mcmc_trace(
    pars = c('alpha','beta1', 'beta2', 'beta3', 'beta4'),
    n_warmup = 500,
    facet_args = list(nrow = 2, labeller = label_parsed)
  )

print(fit, pars = c('alpha','beta1', 'beta2', 'beta3', 'beta4'))
```
```{r}

@@

sim_values <- list(
  N = 6300,                                       # Number of observations.
  K = 2,                                         # Number of groups.
  I = 65,                                         # Number of observation-level covariates.

  male = sample(2, 6300, replace = TRUE),            # Vector of group assignments.
  eth = sample(3, 6300, replace = TRUE),       # Vector of brands covariates.
  age = sample(7, 6300, replace = TRUE),        # Vector of price covariates.
  income = sample(3, 6300, replace = TRUE),
  state = sample(50, 6300, replace = TRUE),

  gamma_mean = 0.5,                              # Mean for the hyperprior on gamma.
  gamma_var = 0.2,                               # Variance for the hyperprior on gamma.
  tau_min = 0,                                   # Minimum for the hyperprior on tau.
  tau_max = .1,                                   # Maximum for the hyperprior on tau.
  sigma_min = 0,                                 # Minimum for the hyperprior on tau.
  sigma_max = .1                                  # Maximum for the hyperprior on tau.
)
# Generate data.
sim_data <- stan(
  file = here::here("Code", "mrp", "generate_data.stan"),
  data = sim_values,
  iter = 10,
  chains = 1,
  seed = 42,
  algorithm = "Fixed_param"
)

# Extract the simulated data.
prior_pc <- tibble(
  service_failure = as.vector(extract(sim_data)$service_failure)
)
# Plot the prior predictive distribution.
prior_pc %>% 
  ggplot(aes(x = service_failure)) +
  geom_density()

Trying to make the simple model work with the data from the vignette. It seems to not be working but the error code is not clear on why it's not working.

```{r}
stan_values <- list(
  N = 1200,                                       # Number of observations.
  K = 2,                                         # Number of groups.
  I = 65,                                         # Number of observation-level covariates.

@@

```{r}
fit3 <- stan(
  file = here::here("Code", "mrp", "logit_simple.stan"),
  data = stan_values,
  seed = 42
)
```

>>>>

```
```{r, eval = FALSE}
fit %>%
  mcmc_trace(
    pars = c('alpha','beta1', 'beta2', 'beta3', 'beta4'),
    n_warmup = 500,
    facet_args = list(nrow = 2, labeller = label_parsed)
  )

print(fit, pars = c('alpha','beta1', 'beta2', 'beta3', 'beta4'))
```

@@

Trying to make the simple model work with the data from the vignette. It seems to not be working but the error code is not clear on why it's not working. 
```{r}
 matrix <- sample %>% 
  select(male, age, eth, income, state)

x <- as.matrix(matrix)
```

```{r}
stan_data <- list(
  N = 1200,                                       # Number of observations.
  K = 6300,                                       # Number of groups.
  g = sample(6300, 1200, replace = TRUE),         # Vector of group assignments

@@

```{r}
data_list <- list(
  D <- 5,                                    # Number of variables. 
  N <- 1200,                                 # Number of observations.
  L <- 6300,                                 # Number of groups. 
  y <- sample$service_failure,               # Outcome variables. 
  ll <- sample(6300, 1200, replace = TRUE),  # Group assignment. 
  x <- as.matrix(matrix)                     # Vector of predictors. 
)
```

```{r, eval = FALSE}
fit <- stan(
  file = here::here("Code", "mrp", "logit_hier.stan"),
  data = data_list,
  seed = 42
)
```
